### 2022-10-10 doc/manuscript/translocation.qmd
Added some potential knowledge gaps to introduction framing

Severe effects of disease on global biodiversity (bats, primates, amphibians, corals, etc.)

@@

-   Tasmanian devils: Epstein et al. (2016)

-   Frogs in Australia: Grogan et al. (2018), McKnight et al. (2020)

@@

@@

@@

>>>>

Severe effects of disease on global biodiversity (bats, primates, amphibians, corals, sea stars, etc.)

@@

-   Species recovery in the face of disease will depend the ability of a species to move or change.

-   Rapid evolution termed "evolutionary rescue" can reverse ongoing declines in some species (Golas et al. 2021; Searle et al. 2021). (Not sure if Allie wants to go the ER direction)

-   ER has been proposed as a mechanism of recovery in wildlife populations decimated by disease (Epstein et al. 2016, Schiebelhut et al. 2018).

-   Tasmanian devils: Epstein et al. (2016), Wells et al., Ecology (2019)

-   Frogs in Australia: Grogan et al. (2018), McKnight et al. (2020), Newell et al. (2013), Scheele et al., Biological Conservation (2014)

@@

-   Sea Star Wasting Disease: Menge et al., Plos One (2016), Schiebelhut et al. PNAS (2018)

-   **Potential knowledge gap**: Subsequent recoveries from disease-induced declines following observed genetic changes have rarely [never?] been documented in wildlife populations.

@@

-   "Rescued" populations provide a source to repatriate extirpated populations and disentangle the effects of the local environment and genetics on host recoveries.

@@

-   **Potential knowledge gap/opportunity/selling point**: For rescued populations to contribute to landscape-scale species recovery, the fitness benefits gained through selection should manifest beyond the natal environment, allowing for the long-term growth and persistence of incipient populations in novel environmental conditions. A unique attribute of this study is that by combining repeated translocations of "rescued" populations, longitudinal surveys, mark-recapture analysis, and population modeling we demonstrate the capacity of "rescued" populations to persist across a landscape of disease. Thus, ER combined with translocations promotes the recovery of a species on the brink of disease-induced extinction.
